Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-24 doc/PRF2022/PRF_main.tex

Supplementary Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} contain the
fully-resolved time courses for the free energy $F$, alignment order
$S_2$, and strain $E$. The eight setups correspond to the four JP
phases---bilayer, vesicle BL, multilamellar, and striated---and two
background flows---shear and TG, and the data are plotted with the same
ordinate to facilitate comparisons between simulation setups. Each setup
considers a range of shear rates $\dot \gamma$ in the interval $[0,
0.2]$ ns$^{-1}$.

The fully-resolved time courses in Supplementary
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} contain significant
oscillations due to the particle-based formulation and tumbling inherent
to the background flows. To extract meaningful data, we further
post-process the $F$, $S_2$, $E$ curves by taking their time average
over the interval $t \in [0, T]$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Free energy}
\label{sec:free-energy}
Figure~\ref{fig:fsummary} plots the time-averaged relative free energy
$\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$
is~\eqref{eq:free_energy2} at $t = 0$. The greatest increase occurs with
the Type II multilamellar phase, with the other phases showing a
moderate change in a few \KBT\,nm$^{-1}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely constant
strains maintained by an external force provided by background flow.
Now we consider dynamic material properties. Specifically, we look at
the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that the shear flow
$\uu_{\infty}^{\text{sh}}$ simulations correspond to a complex fluid
within a drag plate rheometer where the shear stress is set by $\mu
\dot\gamma$ and the observed, sample shear rate is $\dot E$. The
definitions carry over to the TG flow case directly. Also, as a
practical consideration, the rotation of non-isotropic JP phases in the
background flow leads to oscillation in the strain time courses making
systematic fitting challenging (see Supplementary Material
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}). The integral
in~\eqref{eq:strainrate} averages out these oscillations and gives
physically meaningful values.

>>>>

Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the [Supplementary
Material] contain the fully-resolved time courses for the free energy
$F$, alignment order $S_2$, and strain $E$. The eight setups correspond
to the four JP phases---bilayer, vesicle BL, multilamellar, and
striated---and two background flows---shear and TG, and the data are
plotted with the same vertical and horizontal axes to facilitate
comparisons between simulation setups. Each setup considers a range of
shear rates $\dot \gamma$ in the interval $[0, 0.2]$ ns$^{-1}$.

The fully-resolved time courses in
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw} in the [Supplementary
Material] contain significant oscillations due to the particle-based
formulation and tumbling inherent to the background flows. To extract
meaningful data, we further post-process the $F$, $S_2$, $E$ curves by
taking their time average over the interval $t \in [0, T]$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Free energy}
\label{sec:free-energy}
Figure~\ref{fig:fsummary} plots the time-averaged relative free energy
$\frac{1}{T}\int_0^T (F - F_0) \,\dif t$ where $F_0$
is~\eqref{eq:free_energy2} at $t = 0$. The greatest increase occurs with
the Type II multilamellar phase, with the other phases showing a
moderate change in a few \KBT\,nm$^{-1}$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Rheology}
\label{sec:rheology}
So far, we have considered static material properties, namely constant
strains maintained by an external force provided by background flow.
Now we consider dynamic material properties. Specifically, we look at
the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this way is that the shear flow
$\uu_{\infty}^{\text{sh}}$ simulations correspond to a complex fluid
within a drag plate rheometer where the shear stress is set by $\mu
\dot\gamma$ and the observed, sample shear rate is $\dot E$. The
definitions carry over to the TG flow case directly. Also, as a
practical consideration, the rotation of non-isotropic JP phases in the
background flow leads to oscillation in the strain time courses making
systematic fitting challenging (see [Supplementary Material]
Figures~\ref{fig:ulshraw}--\ref{fig:sttgraw}). The integral
in~\eqref{eq:strainrate} averages out these oscillations and gives
physically meaningful values.
